Optical nanostructures design, fabrication, and applications for solar/thermal energy conversion

### 2017-02-12 Submission_2016_source/submission.tex
Fixed refs
Update submission.tex

\begin{keyword}
\texttt{elsarticle.cls}\sep Optical design and fabrication \sep Optical Devices \sep Optics at surfaces \sep Thin Films \sep Solar Energy \sep Subwavelength structures, nanostructures
\end{keyword}

@@

\begin{figure}[ht]
	\includegraphics[width=1\textwidth]{gfig_bbs}
	\caption{\label{gfig_bbs} Spectral emission of a blackbody vs. a selective emitter.  Note that the scales on each graph are in different arbitrary units; the graph is intended to show the relative narrowness of the spectrum using the selective emitter.}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=1\textwidth]{gfig_surfs}
	\caption{\label{gfig_surfs} Types of nanostructured absorbing and 
emitting surfaces: a) random nanotexture b) periodic nanotexture and c) dielectric/metal stack.} 
\end{figure}

@@

In the case of STPV systems, the emitting 
surface will also play a role in device efficiency.  The ideal
surface will be a monochromatic emitter that emits radiation with energy equal to the 
bandgap energy of the PV cell used in the system~\cite{L_AIP_2007}.  Unfortunately, monochromatic 
emitters have a power density of 0, resulting in the requirement of an infinitely large 
emitting surface for practical power generation.  Therefore, in practical STPV systems, an 
emitting surface with a small bandwidth will be desirable~\cite{RF_OptExp_2009}.  
Figure~\ref{Ideal} 
shows the evolution of maximum system efficiency vs. temperature for an ideal system.
\begin{figure}[ht]
\begin{center}
        \includegraphics[width=0.5\textwidth]{ideal_STPV_eff}
        \caption{\label{Ideal} Maximum theoretical efficiency for various system temperatures.  Note the fast increase
around typical operation temperatures for ST and STPV systems.}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
        \includegraphics[width=\textwidth]{Halas_Celanovic}
        \caption{\label{Halas}  Illustration of radiation control using engineered spherical core-shell
nanoparticles {\bf (a)} and multi-layer planar film structures {\bf (b)}.
The absorption, scattering, and extinction cross sections of the core-shell particles can be tuned
across the solar spectrum by changing the ratio of the shell thickness ($r_2$) to the core radius ($r_1$), 
and these
quantities can be computed using Mie theory (see Section {\it 2.2}) for isolated particles, or the 
DDA method (see Section {\it 2.8}) for assemblies of particles.
In {\bf (a)}, the radius of a silica core is fixed at 60 nm, and the thickness of a gold shell is
taken to be 80 nm for curve {\bf a},
70 nm for curve {\bf b}, 67 nm for curve {\bf c}, and 65 nm for curve {\bf d}.
The emittance of several multi-layer structures plotted in {\bf (b)} can be simply computed
using the Transfer Matrix Method (see Section {\it 2.4}); however, 
more sophisticated global device
efficiency considerations were used to identify a photonic crystal on a platinum substrate 
(violet curve in {\bf (b)} as the optimal emitter structure for
an integrated STPV system~\cite{g4}.
Figures reproduced from~\cite{CH_APL_2006} and~\cite{g4} with permission.}
\end{center}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=\textwidth]{Planar}
	\caption{\label{Fan}  Illustration of various planar structures amenable to design and modeling
by transfer matrix methods that serve as selective emitter structures.  
A 1D photonic crystal integrated into a STPV absorber/emitter structure is  
is illustrated in {\bf (a)}. Further details, including absorptivity spectra from this class of structures, can be found
in Fig. 6 and in~\cite{paper1_ref4}.  A Bragg reflector with a single absorbing defect layer,
which supports spectrally selective emission modes, is illustrated in {\bf (b)}. Further details, including emissivity spectra from this class of
structures, can be found in~\cite{BN_JApplPhys_2005}.
A structure that achieves angular and spectral selectivity by coupling evanescent photonic crystal modes
to surface phonon polariton modes in a polar layer is illustrated in {\bf (c)}.  
A structure that achieves angular and spectral selectivity by coupling incident light into Fabry-P\'{e}rot
resonances is illustrated in {\bf (d)}.  Further details, including emissivity spectra from these classes of structures, can 
be found in~\cite{LZ_JApplPhys_2006}.  Figures reproduced from 
~\cite{paper1_ref4, BN_JApplPhys_2005, LZ_JApplPhys_2006} with permission.}

@@

\begin{figure}[ht]
        \includegraphics[width=\textwidth]{FDTD_Modeling}
        \caption{\label{FDTD_Structures}  Illustration of a tungsten structure whose
absorptivity can be tuned by patterning of the surface.  In this example, the tungsten
structure is patterned with nanopyramids with various pyramid heights and with period fixed
at  250 nm.  A representative structure with a pyramid height of 500 nm is shown in {\bf (a)}.
Absorptivities of textured tungsten structures
are plotted in {\bf (b)} for a variety of pyramid heights with the period of the pyramids
fixed at 250 nm.  The finite-difference time-domain (FDTD) method
was used to compute the absorptivities shown in {\bf (b)}.  
Figures reproduced from~\cite{RF_OptExp_2009} with permission.}
\end{figure}

@@

\begin{figure}[ht]
	\includegraphics[width=\textwidth]{gfig12_comb}
	\caption{\label{gfig12_comb} a) AFM photograph of a micromachined double periodic structure with line-widths less than a micron \cite{g29} (reproduced with permission), b) Experimental setup for laser interference lithography, c) SEM image of gratings fabricated by laser interference lithography and etched into quartz \cite{g30} (reproduced with permission), and d) experimental setup for laser sintering of nanoparticles.} %
\end{figure}

@@

\begin{figure}[ht]
	\includegraphics[width=0.65\textwidth]{gfig45_comb}
	\caption{\label{gfig45_comb} a) SEM image of GLAD structures (reprinted with permission) \cite{gfig4ref} and b) and c) SEM images of a laser micro/nano textured Ti surface (reprinted with permission) \cite{g28}.} %
\end{figure}

>>>>

\begin{keyword}
Optical design and fabrication \sep Optical Devices \sep Optics at surfaces \sep Thin Films \sep Solar Energy \sep Subwavelength structures, nanostructures
\end{keyword}

@@

\begin{figure}[ht!]
	\includegraphics[width=1\textwidth]{gfig_bbs}
	\caption{\label{gfig_bbs} Spectral emission of a blackbody vs. a selective emitter.  Note that the scales on each graph are in different arbitrary units; the graph is intended to show the relative narrowness of the spectrum using the selective emitter.}
\end{figure}

\begin{figure}[ht!]
	\includegraphics[width=1\textwidth]{gfig_surfs}
	\caption{\label{gfig_surfs} Types of nanostructured absorbing and 
emitting surfaces: a) random nanotexture b) periodic nanotexture and c) dielectric/metal stack.} 
\end{figure}

@@

In the case of STPV systems, the emitting 
surface will also play a role in device efficiency.  The ideal
surface will be a monochromatic emitter that emits radiation with energy equal to the 
bandgap energy of the PV cell used in the system~\cite{L_AIP_2007}.  Unfortunately, monochromatic 
emitters have a power density of 0, resulting in the requirement of an infinitely large 
emitting surface for practical power generation.  Therefore, in practical STPV systems, an 
emitting surface with a small bandwidth will be desirable~\cite{RF_OptExp_2009}.  
Figure~\ref{Ideal} 
shows the evolution of maximum system efficiency vs. temperature for an ideal system.
\begin{figure}[ht!]
\begin{center}
        \includegraphics[width=0.5\textwidth]{ideal_STPV_eff}
        \caption{\label{Ideal} Maximum theoretical efficiency for various system temperatures.  Note the fast increase
around typical operation temperatures for ST and STPV systems.}
\end{center}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
        \includegraphics[width=\textwidth]{Halas_Celanovic}
        \caption{\label{Halas}  Illustration of radiation control using engineered spherical core-shell
nanoparticles {\bf (a)} and multi-layer planar film structures {\bf (b)}.
The absorption, scattering, and extinction cross sections of the core-shell particles can be tuned
across the solar spectrum by changing the ratio of the shell thickness ($r_2$) to the core radius ($r_1$), 
and these
quantities can be computed using Mie theory (see Section {\it 2.2}) for isolated particles, or the 
DDA method (see Section {\it 2.8}) for assemblies of particles.
In {\bf (a)}, the radius of a silica core is fixed at 60 nm, and the thickness of a gold shell is
taken to be 80 nm for curve {\bf a},
70 nm for curve {\bf b}, 67 nm for curve {\bf c}, and 65 nm for curve {\bf d}.
The emittance of several multi-layer structures plotted in {\bf (b)} can be simply computed
using the Transfer Matrix Method (see Section {\it 2.4}); however, 
more sophisticated global device
efficiency considerations were used to identify a photonic crystal on a platinum substrate 
(violet curve in {\bf (b)} as the optimal emitter structure for
an integrated STPV system~\cite{g4}.
Figures reproduced from~\cite{CH_APL_2006} and~\cite{g4} with permission.}
\end{center}
\end{figure}

\begin{figure}[ht!]
	\includegraphics[width=\textwidth]{Planar}
	\caption{\label{Fan}  Illustration of various planar structures amenable to design and modeling
by transfer matrix methods that serve as selective emitter structures.  
A 1D photonic crystal integrated into a STPV absorber/emitter structure is  
is illustrated in {\bf (a)}. Further details, including absorptivity spectra from this class of structures, can be found
in Fig. 6 and in~\cite{paper1_ref4}.  A Bragg reflector with a single absorbing defect layer,
which supports spectrally selective emission modes, is illustrated in {\bf (b)}. Further details, including emissivity spectra from this class of
structures, can be found in~\cite{BN_JApplPhys_2005}.
A structure that achieves angular and spectral selectivity by coupling evanescent photonic crystal modes
to surface phonon polariton modes in a polar layer is illustrated in {\bf (c)}.  
A structure that achieves angular and spectral selectivity by coupling incident light into Fabry-P\'{e}rot
resonances is illustrated in {\bf (d)}.  Further details, including emissivity spectra from these classes of structures, can 
be found in~\cite{LZ_JApplPhys_2006}.  Figures reproduced from 
~\cite{paper1_ref4, BN_JApplPhys_2005, LZ_JApplPhys_2006} with permission.}

@@

\begin{figure}[ht!]
        \includegraphics[width=\textwidth]{FDTD_Modeling}
        \caption{\label{FDTD_Structures}  Illustration of a tungsten structure whose
absorptivity can be tuned by patterning of the surface.  In this example, the tungsten
structure is patterned with nanopyramids with various pyramid heights and with period fixed
at  250 nm.  A representative structure with a pyramid height of 500 nm is shown in {\bf (a)}.
Absorptivities of textured tungsten structures
are plotted in {\bf (b)} for a variety of pyramid heights with the period of the pyramids
fixed at 250 nm.  The finite-difference time-domain (FDTD) method
was used to compute the absorptivities shown in {\bf (b)}.  
Figures reproduced from~\cite{RF_OptExp_2009} with permission.}
\end{figure}

@@

\begin{figure}[ht!]
	\includegraphics[width=\textwidth]{gfig12_comb}
	\caption{\label{gfig12_comb} a) AFM photograph of a micromachined double periodic structure with line-widths less than a micron \cite{g29} (reproduced with permission), b) Experimental setup for laser interference lithography, c) SEM image of gratings fabricated by laser interference lithography and etched into quartz \cite{g30} (reproduced with permission), and d) experimental setup for laser sintering of nanoparticles.} %
\end{figure}

@@

\begin{figure}[ht!]
	\includegraphics[width=0.65\textwidth]{gfig45_comb}
	\caption{\label{gfig45_comb} a) SEM image of GLAD structures (reprinted with permission) \cite{gfig4ref} and b) and c) SEM images of a laser micro/nano textured Ti surface (reprinted with permission) \cite{g28}.} %
\end{figure}
